---
title: "Changes in CRAN submissions in the age of LLMs"
date: "2026-05-11"
description: |
  A brief look at data on CRAN submissions over time.
categories: [r]
editor:
  markdown:
    wrap: sentence
knitr:
  opts_chunk:
    echo: false
    warning: false
---

This is more data on CRAN submissions in 2026, to support and follow-up on the [DDSS blog](https://princeton-ddss.github.io/notes/cran-growth).

```{r}
#| label: setup
suppressPackageStartupMessages({
  library(geomtextpath)
  library(tidyverse)
  library(wacolors)
})

raw_db <- tools::CRAN_package_db() |>
  as_tibble()

current_pkgs <- raw_db |>
  select(Package, Published, Maintainer) |>
  mutate(
    Published = as.Date(Published),
    Maintainer = str_remove(Maintainer, '\\s*<[^>]+>') |> str_squish()
  ) |>
  distinct(Package, .keep_all = TRUE)

archive_rds <- tempfile(fileext = '.rds')
download.file(
  'https://cran.r-project.org/src/contrib/Meta/archive.rds',
  archive_rds,
  mode = 'wb'
)
archive <- readRDS(archive_rds)

archive_all <- lapply(names(archive), \(pkg) {
  tibble(Package = pkg, date = as.Date(archive[[pkg]]$mtime))
}) |>
  list_rbind()

archive_first <- archive_all |>
  group_by(Package) |>
  summarize(archive_first = min(date), .groups = 'drop')

all_pkgs <- current_pkgs |>
  full_join(archive_first, by = 'Package') |>
  mutate(
    first_published = coalesce(archive_first, Published)
  )

new_by_month <- all_pkgs |>
  filter(
    !is.na(first_published),
    first_published >= as.Date('2016-01-01')
  ) |>
  mutate(
    year = year(first_published),
    month = month(first_published)
  ) |>
  count(year, month, name = 'n_new')

all_submissions <- bind_rows(
  archive_all,
  current_pkgs |> rename(date = Published)
) |>
  filter(!is.na(date))

parse_authors <- function(x) {
  if (is.na(x) || !nzchar(x)) {
    return(character(0))
  }
  tryCatch(
    {
      persons <- eval(parse(text = x))
      keep <- vapply(
        seq_along(persons),
        \(i) {
          roles <- persons[[i]]$role
          !is.null(roles) && any(roles %in% c('aut', 'cre'))
        },
        logical(1)
      )
      format(persons[keep], include = c('given', 'family')) |>
        str_squish() |>
        discard(\(n) n == '' | n == 'NA')
    },
    error = \(e) character(0)
  )
}

pkg_authors <- raw_db |>
  select(Package, `Authors@R`) |>
  mutate(author = lapply(`Authors@R`, parse_authors)) |>
  select(-`Authors@R`) |>
  unnest(author)

author_pkgs <- pkg_authors |>
  left_join(all_pkgs |> select(Package, first_published), by = 'Package') |>
  filter(!is.na(first_published), !is.na(author), nzchar(author))

parse_deps <- function(x) {
  if (is.na(x) || !nzchar(x)) {
    return(character(0))
  }
  strsplit(x, ',')[[1]] |>
    str_remove('\\(.*\\)') |>
    str_squish() |>
    discard(\(d) d == '' | d == 'R')
}

author_debut <- author_pkgs |>
  group_by(author) |>
  summarize(author_debut = min(first_published), .groups = 'drop')

pkg_author_novelty <- author_pkgs |>
  left_join(author_debut, by = 'author') |>
  mutate(author_is_new = author_debut >= first_published) |>
  group_by(Package, first_published) |>
  summarize(
    n_authors = n(),
    n_new_authors = sum(author_is_new),
    all_authors_new = all(author_is_new),
    .groups = 'drop'
  )

newcomer_by_year <- pkg_author_novelty |>
  filter(!is.na(first_published), year(first_published) >= 2010) |>
  mutate(year = year(first_published)) |>
  group_by(year) |>
  summarize(
    n_pkgs = n(),
    n_all_new = sum(all_authors_new),
    pct_all_new = mean(all_authors_new),
    .groups = 'drop'
  ) |>
  filter(year <= year(today()))

author_count <- author_pkgs |>
  group_by(Package, first_published) |>
  summarize(n_authors = n_distinct(author), .groups = 'drop') |>
  filter(!is.na(first_published), year(first_published) >= 2010)

pkg_deps <- raw_db |>
  select(Package, Imports, Depends, Suggests) |>
  mutate(
    imports = lapply(Imports, parse_deps),
    depends = lapply(Depends, parse_deps),
    suggests = lapply(Suggests, parse_deps),
    n_imports = lengths(imports),
    n_depends = lengths(depends),
    n_suggests = lengths(suggests),
    n_hard_deps = n_imports + n_depends
  ) |>
  left_join(all_pkgs |> select(Package, first_published), by = 'Package') |>
  filter(!is.na(first_published), year(first_published) >= 2010)

pkg_size <- raw_db |>
  select(Package, VignetteBuilder, NeedsCompilation) |>
  mutate(
    has_vignette = !is.na(VignetteBuilder),
    needs_compilation = !is.na(NeedsCompilation) & NeedsCompilation == 'yes'
  ) |>
  left_join(
    pkg_deps |> select(Package, n_hard_deps, n_suggests),
    by = 'Package'
  ) |>
  left_join(all_pkgs |> select(Package, first_published), by = 'Package') |>
  filter(!is.na(first_published), year(first_published) >= 2010)

size_by_year <- pkg_size |>
  mutate(year = year(first_published)) |>
  group_by(year) |>
  summarize(
    pct_vignette = mean(has_vignette, na.rm = TRUE),
    pct_compiled = mean(needs_compilation, na.rm = TRUE),
    .groups = 'drop'
  ) |>
  filter(year <= year(today()))

top_maintainers_current <- current_pkgs |>
  count(Maintainer, sort = TRUE) |>
  slice_head(n = 200) |>
  pull(Maintainer)

top10 <- top_maintainers_current[1:10]

top10_2008 <- all_pkgs |>
  filter(
    !is.na(first_published),
    !is.na(Maintainer),
    first_published <= as.Date('2008-12-31')
  ) |>
  count(Maintainer, sort = TRUE) |>
  slice_head(n = 10) |>
  pull(Maintainer)

top_maintainers <- union(top_maintainers_current, top10_2008)

era_levels <- c(
  '97-00',
  '01-04',
  '05-08',
  '09-12',
  '13-16',
  '17-20',
  '21-24',
  '25+'
)

maintainer_era <- all_pkgs |>
  filter(Maintainer %in% top_maintainers, !is.na(first_published)) |>
  group_by(Maintainer) |>
  summarize(first_appearance = min(first_published), .groups = 'drop') |>
  mutate(
    era = case_when(
      year(first_appearance) <= 2000 ~ '97-00',
      year(first_appearance) <= 2004 ~ '01-04',
      year(first_appearance) <= 2008 ~ '05-08',
      year(first_appearance) <= 2012 ~ '09-12',
      year(first_appearance) <= 2016 ~ '13-16',
      year(first_appearance) <= 2020 ~ '17-20',
      year(first_appearance) <= 2024 ~ '21-24',
      .default = '25+'
    ) |>
      factor(levels = era_levels)
  )

cumulative_data <- all_pkgs |>
  filter(Maintainer %in% top_maintainers, !is.na(first_published)) |>
  mutate(year_month = floor_date(first_published, 'month')) |>
  count(Maintainer, year_month, name = 'n_new') |>
  arrange(Maintainer, year_month) |>
  mutate(cumulative = cumsum(n_new), .by = Maintainer) |>
  left_join(maintainer_era, by = 'Maintainer')

top_authors_current <- pkg_authors |>
  count(author, sort = TRUE) |>
  slice_head(n = 200) |>
  pull(author)

top_authors_10 <- top_authors_current[1:10]

top_authors_2008 <- author_pkgs |>
  filter(first_published <= as.Date('2008-12-31')) |>
  count(author, sort = TRUE) |>
  slice_head(n = 10) |>
  pull(author)

top_authors <- union(top_authors_current, top_authors_2008)

author_era <- author_pkgs |>
  filter(author %in% top_authors) |>
  group_by(author) |>
  summarize(first_appearance = min(first_published), .groups = 'drop') |>
  mutate(
    era = case_when(
      year(first_appearance) <= 2000 ~ '97-00',
      year(first_appearance) <= 2004 ~ '01-04',
      year(first_appearance) <= 2008 ~ '05-08',
      year(first_appearance) <= 2012 ~ '09-12',
      year(first_appearance) <= 2016 ~ '13-16',
      year(first_appearance) <= 2020 ~ '17-20',
      year(first_appearance) <= 2024 ~ '21-24',
      .default = '25+'
    ) |>
      factor(levels = era_levels)
  )

author_cumulative <- author_pkgs |>
  filter(author %in% top_authors) |>
  mutate(year_month = floor_date(first_published, 'month')) |>
  count(author, year_month, name = 'n_new') |>
  arrange(author, year_month) |>
  mutate(cumulative = cumsum(n_new), .by = author) |>
  left_join(author_era, by = 'author')

month_week_breaks <- isoweek(as.Date(paste0(
  '2019-',
  formatC(1:12, width = 2, flag = '0'),
  '-01'
)))

may7_filter <- \(df) {
  filter(df, month(date) < 5 | (month(date) == 5 & day(date) <= 7))
}
```

New package submissions are taking off in 2026:

```{r}
#| label: fig-new-packages-by-month
new_by_month |>
  filter(
    (year < as.integer(year(today()))) |
      (year <= as.integer(year(today())) & month < as.integer(month(today())))
  ) |>
  ggplot() +
  geom_line(aes(x = month, y = n_new, color = factor(year), group = year)) +
  geom_point(aes(x = month, y = n_new, color = factor(year), group = year)) +
  scale_x_continuous(
    name = NULL,
    breaks = 1:12,
    labels = month.abb,
    minor_breaks = NULL
  ) +
  scale_color_viridis_d(option = 'turbo', direction = -1) +
  labs(
    title = 'New CRAN packages per month',
    subtitle = 'Year-over-year comparison since 2016',
    y = 'New packages',
    color = 'Year'
  ) +
  theme_bw(base_family = 'Inter')
```

Monthly package submissions, including updates, are up:

```{r}
#| label: fig-all-submissions-by-month
all_submissions |>
  filter(
    date >= as.Date('2016-01-01'),
    date < as.Date(x = paste0('2026-', month(today()), '-01'))
  ) |>
  mutate(year = year(date), month = month(date)) |>
  count(year, month, name = 'n') |>
  ggplot() +
  geom_line(aes(x = month, y = n, color = factor(year), group = year)) +
  geom_point(aes(x = month, y = n, color = factor(year), group = year)) +
  scale_x_continuous(
    name = NULL,
    breaks = 1:12,
    labels = month.abb,
    minor_breaks = NULL
  ) +
  scale_color_viridis_d(option = 'turbo', direction = -1) +
  labs(
    title = 'All CRAN submissions per month',
    subtitle = 'Year-over-year comparison since 2016',
    y = 'Submissions',
    color = 'Year'
  ) +
  theme_bw(base_family = 'Inter')
```

Increases are relatively consistent across weeks:

```{r}
#| label: fig-all-submissions-by-week
all_submissions |>
  filter(date >= as.Date('2016-01-01')) |>
  mutate(year = isoyear(date), week = isoweek(date)) |>
  count(year, week, name = 'n') |>
  ggplot() +
  geom_line(
    aes(x = week, y = n, color = factor(year), group = year),
    linewidth = 0.5
  ) +
  geom_point(
    aes(x = week, y = n, color = factor(year), group = year),
    size = 1
  ) +
  scale_x_continuous(
    name = NULL,
    breaks = month_week_breaks,
    labels = month.abb,
    minor_breaks = NULL
  ) +
  scale_color_viridis_d(option = 'turbo', direction = -1) +
  labs(
    title = 'All CRAN submissions per week',
    subtitle = 'Year-over-year comparison since 2016',
    y = 'Submissions',
    color = 'Year'
  ) +
  theme_bw(base_family = 'Inter')
```

All package submissions are trending up in 2026:

```{r}
#| label: fig-all-submissions-through-may7
all_submissions |>
  may7_filter() |>
  count(year = year(date), name = 'n') |>
  ggplot() +
  geom_col(aes(x = year, y = n)) +
  scale_x_continuous(breaks = scales::breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(
    name = 'Submissions',
    breaks = scales::pretty_breaks(),
    labels = scales::label_comma()
  ) +
  labs(
    title = 'All CRAN submissions through May 7, by year',
    x = NULL
  ) +
  theme_bw(base_family = 'Inter') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

New package submissions are way above expectations:

```{r}
#| label: fig-new-packages-through-may7
all_pkgs |>
  rename(date = first_published) |>
  may7_filter() |>
  count(year = year(date), name = 'n') |>
  ggplot() +
  geom_col(aes(x = year, y = n)) +
  scale_x_continuous(breaks = scales::breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(
    name = 'New packages',
    breaks = scales::pretty_breaks(n = 8),
    labels = scales::label_comma()
  ) +
  labs(
    title = 'New CRAN packages through May 7, by year',
    x = NULL
  ) +
  theme_bw(base_family = 'Inter') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

CRAN submissions from new authors have stayed relatively stable over time, with perhaps a dip in recent years:

```{r}
#| label: fig-newcomer-authors-by-year
newcomer_by_year |>
  ggplot() +
  geom_col(aes(x = year, y = pct_all_new)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'Percent all-newcomer packages',
    labels = scales::label_percent(),
    breaks = scales::pretty_breaks()
  ) +
  labs(
    title = 'Packages where all authors are CRAN newcomers',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

There's a big increase in solo-authored new packages in 2026:

```{r}
#| label: fig-author-count-share-by-year
author_count |>
  filter(year(first_published) <= year(today())) |>
  mutate(
    year = year(first_published),
    n_authors_cat = factor(
      case_when(
        n_authors == 1 ~ '1',
        n_authors == 2 ~ '2',
        n_authors == 3 ~ '3',
        n_authors >= 4 ~ '4+'
      ),
      levels = c('4+', '3', '2', '1')
    )
  ) |>
  count(year, n_authors_cat) |>
  group_by(year) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot() +
  geom_col(aes(x = year, y = pct, fill = n_authors_cat)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'Percent of packages',
    labels = scales::label_percent()
  ) +
  scale_fill_wa_d('puget', name = 'Authors') +
  labs(
    title = 'Author count per new package by year',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

If the trend continues, single authored packages in 2026 would nearly double that of 2025:

```{r}
#| label: fig-author-count-projected-by-year
author_count |>
  filter(year(first_published) <= year(today())) |>
  mutate(
    year = year(first_published),
    n_authors_cat = factor(
      case_when(
        n_authors == 1 ~ '1',
        n_authors == 2 ~ '2',
        n_authors == 3 ~ '3',
        n_authors >= 4 ~ '4+'
      ),
      levels = c('4+', '3', '2', '1')
    )
  ) |>
  count(year, n_authors_cat) |>
  mutate(n = if_else(year == year(today()), n * 12 / 5, n)) |>
  ggplot() +
  geom_line(
    aes(x = year, y = n, color = n_authors_cat),
    data = \(d) filter(d, year < year(today()))
  ) +
  geom_line(
    aes(x = year, y = n, color = n_authors_cat),
    data = \(d) filter(d, year >= year(today()) - 1),
    linetype = 'dotted'
  ) +
  geom_point(aes(x = year, y = n, color = n_authors_cat)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'New packages',
    labels = scales::label_comma(),
    limits = c(0, NA)
  ) +
  scale_color_wa_d('puget', name = 'Authors') +
  labs(
    title = 'Author count per new package by year',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

This is being driven by solo developers who have previously published packages on CRAN:

```{r}
#| label: fig-author-profile-share-by-year
pkg_author_novelty |>
  filter(
    !is.na(first_published),
    year(first_published) >= 2010,
    year(first_published) <= year(today())
  ) |>
  mutate(
    year = year(first_published),
    pkg_type = factor(
      case_when(
        n_authors == 1 & all_authors_new ~ 'Solo newcomer',
        n_authors == 1 & !all_authors_new ~ 'Solo experienced',
        n_authors > 1 ~ 'Multi-author'
      ),
      levels = c('Multi-author', 'Solo experienced', 'Solo newcomer')
    )
  ) |>
  count(year, pkg_type) |>
  group_by(year) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot() +
  geom_col(aes(x = year, y = pct, fill = pkg_type)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'Percent of packages',
    labels = scales::label_percent()
  ) +
  scale_fill_wa_d('puget', name = NULL) +
  labs(
    title = 'New packages by author profile',
    subtitle = 'By year of first CRAN submission; structured Authors@R only'
  ) +
  theme_bw(base_family = 'Inter')
```

If the trends continue, experienced developers would nearly hit the same number of packages as multi-author teams:

```{r}
#| label: fig-author-profile-projected-by-year
pkg_author_novelty |>
  filter(
    !is.na(first_published),
    year(first_published) >= 2010,
    year(first_published) <= year(today())
  ) |>
  mutate(
    year = year(first_published),
    pkg_type = factor(
      case_when(
        n_authors == 1 & all_authors_new ~ 'Solo newcomer',
        n_authors == 1 & !all_authors_new ~ 'Solo experienced',
        n_authors > 1 ~ 'Multi-author'
      ),
      levels = c('Multi-author', 'Solo experienced', 'Solo newcomer')
    )
  ) |>
  count(year, pkg_type) |>
  mutate(n = if_else(year == year(today()), n * 12 / 5, n)) |>
  ggplot() +
  geom_line(aes(x = year, y = n, color = pkg_type), data = \(d) {
    filter(d, year < year(today()))
  }) +
  geom_line(
    aes(x = year, y = n, color = pkg_type),
    data = \(d) filter(d, year >= year(today()) - 1),
    linetype = 'dotted'
  ) +
  geom_point(aes(x = year, y = n, color = pkg_type)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'New packages',
    labels = scales::label_comma(),
    limits = c(0, NA)
  ) +
  scale_color_wa_d('puget', name = NULL) +
  labs(
    title = 'New packages by author profile',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

There's been a small increase in the number of dependencies over time, especially from none to 1 or 2:

```{r}
#| label: fig-hard-dependencies-by-year
pkg_deps |>
  filter(year(first_published) <= year(today())) |>
  mutate(
    year = year(first_published),
    deps_cat = factor(
      case_when(
        n_hard_deps == 0 ~ '0',
        n_hard_deps == 1 ~ '1',
        n_hard_deps == 2 ~ '2',
        n_hard_deps == 3 ~ '3',
        n_hard_deps == 4 ~ '4',
        n_hard_deps == 5 ~ '5',
        n_hard_deps <= 10 ~ '6-10',
        TRUE ~ '11+'
      ),
      levels = c('11+', '6-10', '5', '4', '3', '2', '1', '0')
    )
  ) |>
  count(year, deps_cat) |>
  group_by(year) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot() +
  geom_col(aes(x = year, y = pct, fill = deps_cat)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'Percent of packages',
    labels = scales::label_percent()
  ) +
  scale_fill_wa_d('puget', name = 'Deps') +
  labs(
    title = 'Hard dependencies per new package',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

Yet, data suggests packages are both becoming simpler and better documented, using some basic proxies:

```{r}
#| label: fig-complexity-indicators-by-year
size_by_year |>
  pivot_longer(
    c(pct_vignette, pct_compiled),
    names_to = 'metric',
    values_to = 'value'
  ) |>
  mutate(
    metric = case_when(
      metric == 'pct_vignette' ~ 'Has vignette',
      metric == 'pct_compiled' ~ 'Needs compilation'
    )
  ) |>
  ggplot() +
  geom_line(aes(x = year, y = value, color = metric)) +
  geom_point(aes(x = year, y = value, color = metric)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = NULL,
    labels = scales::label_percent(),
    limits = c(0, NA)
  ) +
  scale_color_wa_d('puget', name = NULL) +
  labs(
    title = 'Package complexity indicators over time',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

Packages are also including more suggested packages:

```{r}
#| label: fig-suggested-dependencies-by-year
pkg_size |>
  filter(year(first_published) <= year(today())) |>
  mutate(
    year = year(first_published),
    suggests_cat = factor(
      case_when(
        n_suggests == 0 ~ '0',
        n_suggests == 1 ~ '1',
        n_suggests == 2 ~ '2',
        n_suggests == 3 ~ '3',
        n_suggests == 4 ~ '4',
        n_suggests == 5 ~ '5',
        n_suggests <= 10 ~ '6-10',
        TRUE ~ '11+'
      ),
      levels = c('11+', '6-10', '5', '4', '3', '2', '1', '0')
    )
  ) |>
  count(year, suggests_cat) |>
  group_by(year) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot() +
  geom_col(aes(x = year, y = pct, fill = suggests_cat)) +
  scale_x_continuous(
    name = NULL,
    breaks = scales::breaks_width(2),
    minor_breaks = NULL
  ) +
  scale_y_continuous(
    name = 'Percent of packages',
    labels = scales::label_percent()
  ) +
  scale_fill_wa_d('puget', name = 'Suggests') +
  labs(
    title = 'Suggested dependencies per new package',
    subtitle = 'By year of first CRAN submission'
  ) +
  theme_bw(base_family = 'Inter')
```

Over the longer period of CRAN, we can see a change in contributions towards the `tidyverse` and `Rcpp` by looking at maintainers:

```{r}
#| label: fig-cumulative-packages-by-maintainer
cumulative_data |>
  ggplot() +
  geom_line(
    aes(x = year_month, y = cumulative, group = Maintainer, color = era),
    data = \(d) filter(d, !Maintainer %in% c(top10, top10_2008)),
    alpha = 0.4,
    linewidth = 0.4
  ) +
  geom_line(
    aes(x = year_month, y = cumulative, group = Maintainer, color = era),
    data = \(d) filter(d, Maintainer %in% top10_2008, !Maintainer %in% top10),
    alpha = 0.7,
    linewidth = 0.5
  ) +
  geom_textline(
    aes(
      x = year_month,
      y = cumulative,
      group = Maintainer,
      color = era,
      label = Maintainer
    ),
    data = \(d) filter(d, Maintainer %in% top10_2008, !Maintainer %in% top10),
    linewidth = 0.5,
    size = 3,
    hjust = (2008 - 1997) / (2026 - 1997),
    key_glyph = 'path'
  ) +
  geom_textline(
    aes(
      x = year_month,
      y = cumulative,
      group = Maintainer,
      color = era,
      label = Maintainer
    ),
    data = \(d) filter(d, Maintainer %in% top10),
    size = 3,
    hjust = 0.85,
    key_glyph = 'path'
  ) +
  scale_x_date(
    date_breaks = '2 years',
    date_labels = '%Y',
    minor_breaks = NULL
  ) +
  scale_color_wa_d('puget') +
  labs(
    title = 'Cumulative packages by maintainer over time',
    subtitle = 'Top 200 current maintainers; labeled at current top 10 and 2008 top 10',
    x = NULL,
    y = 'Number of packages',
    color = 'First active'
  ) +
  theme_bw(base_family = 'Inter') +
  theme(
    legend.position = c(0.02, 0.98),
    legend.justification = c(0, 1),
    legend.background = element_rect(fill = alpha('white', 0.7), color = NA)
  )
```

Looking at authors, instead of just maintainers, highlights the RStudio/Posit contribution in the growing ecosystem:

```{r}
#| label: fig-cumulative-packages-by-author
author_cumulative |>
  ggplot() +
  geom_line(
    aes(x = year_month, y = cumulative, group = author, color = era),
    data = \(d) filter(d, !author %in% c(top_authors_10, top_authors_2008)),
    alpha = 0.4,
    linewidth = 0.4
  ) +
  geom_line(
    aes(x = year_month, y = cumulative, group = author, color = era),
    data = \(d) {
      filter(d, author %in% top_authors_2008, !author %in% top_authors_10)
    },
    alpha = 0.7,
    linewidth = 0.5
  ) +
  geom_textline(
    aes(
      x = year_month,
      y = cumulative,
      group = author,
      color = era,
      label = author
    ),
    data = \(d) {
      filter(d, author %in% top_authors_2008, !author %in% top_authors_10)
    },
    linewidth = 0.5,
    size = 3,
    hjust = (2008 - 1997) / (2026 - 1997),
    key_glyph = 'path'
  ) +
  geom_textline(
    aes(
      x = year_month,
      y = cumulative,
      group = author,
      color = era,
      label = author
    ),
    data = \(d) filter(d, author %in% top_authors_10),
    linewidth = 0.8,
    size = 3,
    hjust = 0.85,
    key_glyph = 'path'
  ) +
  scale_x_date(
    date_breaks = '2 years',
    date_labels = '%Y',
    minor_breaks = NULL
  ) +
  scale_color_wa_d('sound_sunset', drop = FALSE) +
  labs(
    title = 'Cumulative packages by author over time',
    subtitle = 'Top 200 current authors (aut/cre); labeled at current top 10 and 2008 top 10',
    x = NULL,
    y = 'Cumulative packages',
    color = 'First active'
  ) +
  theme_bw(base_family = 'Inter') +
  theme(
    legend.position = c(0.02, 0.98),
    legend.justification = c(0, 1),
    legend.background = element_rect(fill = alpha('white', 0.7), color = NA)
  )
```
